---
title: "conda speed tests"
author: John Blischak
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, error = TRUE)
library(fs)
library(stringr)
```

## Motivation

The conda package and environment manager is extremely useful. I've invested a
lot of time maintaining R packages for the conda-forge channel and helping
others adopt conda for their projects. However, recent versions have become
extremely slow ([Issue #7239][7239], [Issue #8291][8291]). One advantage of conda
over a more heavy weight option like Docker/singularity is that it is much
easier to create new environments or add/remove specific packages, but this
advantage is lost if it takes 30 minutes to install a package. I have been using
conda to configure the environment for CI builds, but now the initial conda step
either takes up most of the available CI time, or more often than not it stalls.

[7239]: https://github.com/conda/conda/issues/7239
[8291]: https://github.com/conda/conda/issues/8291

## Overview

I have created a GitHub repository [conda-speed-tests][] and configured a
[CircleCI workflow][circle] to time conda commands for my common use cases.
Specifically, I tested the following versions of conda:

* Latest release
* Latest commit

```{r versions}
files <- dir_ls("log")
versions <- files
versions <- str_replace(versions, "^log/", "")
versions <- str_replace(versions, ".txt$", "")
versions <- str_extract(versions, "[\\.,a-z,0-9]+$")
versions
```

For the following use cases:

* [Install numpy from defaults channel][]
* [Install numpy from conda-forge][]
* [Install scikit-learn from defaults][]
* [Install scikit-learn from conda-forge][]
* [Install r-base from defaults][]
* [Install r-base from conda-forge][]
* [Install r-devtools from defaults][]
* [Install r-devtools from conda-forge][]
* [Install bioconductor-biobase from bioconda][]
* [Install bioconductor-limma from bioconda][]
* [Install r-workflowr from jdblischak][]
* [Install bioconductor-scde from jdblischak][]

[conda-speed-tests]: https://github.com/jdblischak/conda-speed-tests
[circle]: https://circleci.com/gh/jdblischak/conda-speed-tests

## Install numpy from defaults channel

```{r numpy-defaults}
files <- dir_ls("time", glob = "numpy-defaults*")
for (f in files) {
  print(f)
  print(readLines(f))
}
```

```
conda install numpy
```

## Install numpy from conda-forge

```{r numpy-cf}
files <- dir_ls("time", glob = "numpy-cf*")
for (f in files) {
  print(f)
  print(readLines(f))
}
```

```
conda install -c conda-forge numpy
```

## Install scikit-learn from defaults

```
conda install scikit-learn
```

## Install scikit-learn from conda-forge

```
conda install -c conda-forge scikit-learn
```

## Install r-base from defaults

```
conda install r-base
```

## Install r-base from conda-forge

```
conda install -c conda-forge r-base
```

## Install r-devtools from defaults

```
conda install r-devtools
```

## Install r-devtools from conda-forge

```
conda install -c conda-forge r-devtools
```

## Install bioconductor-biobase from bioconda

```
conda install -c conda-forge -c bioconda bioconductor-biobase
```

## Install bioconductor-limma from bioconda

```
conda install -c conda-forge -c bioconda bioconductor-limma
```

## Install r-workflowr from jdblischak

```
conda install -c conda-forge -c jdblischak r-workflowr=0.11.0
```

## Install bioconductor-scde from jdblischak

```
conda install -c conda-forge -c bioconda -c jdblischak bioconductor-scde=1.99.1
```
