---
title: "conda speed tests"
author: John Blischak
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
library(dplyr)
library(fs)
library(ggplot2)
library(glue)
library(stringr)
```

## Motivation

The conda package and environment manager is extremely useful. I've invested a
lot of time maintaining R packages for the conda-forge channel and helping
others adopt conda for their projects. However, recent versions have become
extremely slow ([Issue #7239][7239], [Issue #8291][8291]). One advantage of conda
over a more heavy weight option like Docker/singularity is that it is much
easier to create new environments or add/remove specific packages, but this
advantage is lost if it takes 30 minutes to install a package. I have been using
conda to configure the environment for CI builds, but now the initial conda step
either takes up most of the available CI time, or more often than not it stalls.

[7239]: https://github.com/conda/conda/issues/7239
[8291]: https://github.com/conda/conda/issues/8291

## Overview

I have created a GitHub repository [conda-speed-tests][] and configured a
[CircleCI workflow][circle] to time conda commands for my common use cases.

[conda-speed-tests]: https://github.com/jdblischak/conda-speed-tests
[circle]: https://circleci.com/gh/jdblischak/conda-speed-tests

```{r versions}
files <- dir_ls("log", glob = "*package_*.txt")
files_split <- str_split_fixed(files, "_", n = 3)
ids <- unique(files_split[, 2])
versions <- unique(str_replace(files_split[, 3], ".txt$", ""))
```

```{r}
list_instrument <- list()
```


## numpy-defaults

```{r}
id <- ids[1]
for (v in versions) {
  instrument <- read.csv(glue::glue("log/instrumentation-record_{id}_{v}.csv"),
                         header = FALSE, stringsAsFactors = FALSE)
  instrument[["version"]] <- v
  list_instrument[[id]] <- rbind(list_instrument[[id]], instrument)
}
colnames(list_instrument[[id]]) <- c("step", "time", "version")
```

```{r}
ggplot(list_instrument[[id]], aes(x = step, y = time)) +
  geom_point() +
  facet_wrap(~version, scales = "free_x") +
  labs(title = id)
```

```{r}
total <- list_instrument[[id]] %>%
  group_by(version) %>%
  summarize(time = sum(time))
ggplot(total, aes(x = version, y = time)) +
  geom_point() +
  labs(title = id)
```

```{r results='asis'}
config <- readLines(glue::glue("log/conda-config_{id}_{v}.txt"))
config <- paste(config, collapse = "\n")
glue::glue("
<details>
<summary>
Output of <code>conda config --show-sources</code>
</summary>
<code>
{config}
</code>
</details>
"
)
```
